\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-12-23 motivation.tex
overall updates

\Azure Storage vNext is the next generation storage system for \Microsoft \Azure, where the primary design target is to scale the storage capacity by more than 100$\times$. Similar to the current system, vNext employs containers, called \emph{extents}, to store data. Extents are typically several gigabytes each, consisting of many data blocks, and replicated over multiple \emph{Extent Nodes} (ENs). However, in contrast to the current system, which employs a Paxos-based, centralized mapping from extents to ENs, vNext achieves its scalability target by employing a \emph{distributed mapping}. In vNext, extents are divided into partitions, with each partition managed by a light-weight \emph{Extent Manager} (ExtMgr). This partitioning is illustrated in Figure~\ref{fig:vnext}.

>>>>

\Azure Storage vNext is the next generation storage system for \Microsoft \Azure, where the primary design target is to scale the storage capacity by more than 100$\times$. Similar to the current system, vNext employs containers, called \emph{extents}, to store data. Extents can be several gigabytes each, consisting of many data blocks, and are replicated over multiple \emph{Extent Nodes} (ENs). However, in contrast to the current system, which uses a Paxos-based, centralized mapping from extents to ENs, vNext achieves scalability by using a \emph{distributed mapping}. In vNext, extents are divided into partitions, with each partition managed by a light-weight \emph{Extent Manager} (ExtMgr). This partitioning is illustrated in Figure~\ref{fig:vnext}.
